---
title: "Getting Started with ggpubfigs"
author: "Jacob L. Steenwyk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Getting Started with ggpubfigs}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(ggplot2)
library(ggpubfigs)

scatter_by_species <- function(th) {
  ggplot(iris, aes(Sepal.Length, Petal.Width, color = Species)) +
    geom_point() +
    th
}

histo_by_species <- function(th) {
  ggplot(iris, aes(Sepal.Length, fill = Species)) +
    geom_histogram(bins = 20) +
    th
}
```

`ggpubfigs` is a lightweight extension to `ggplot2` focused on:

- publication-ready themes
- presentation-ready themes
- colorblind-friendly palettes

This vignette shows all exported themes and the most common palette workflows.

## Theme Overview

`ggpubfigs` currently exports 8 themes:

- Publication themes: `theme_grid()`, `theme_simple()`, `theme_grey()`
- Presentation themes: `theme_black()`, `theme_blue()`, `theme_red()`
- Larger-font themes: `theme_big_grid()`, `theme_big_simple()`

## Quick Start

```{r}
ggplot(mtcars, aes(factor(carb), fill = factor(cyl))) +
  geom_bar() +
  scale_fill_manual(values = friendly_pal("ito_seven")) +
  theme_big_simple()
```

## Publication Themes

### `theme_grid()`

```{r}
scatter_by_species(theme_grid())
```

### `theme_simple()`

```{r}
scatter_by_species(theme_simple())
```

### `theme_grey()`

```{r}
scatter_by_species(theme_grey())
```

## Presentation Themes

### `theme_black()`

```{r}
scatter_by_species(theme_black())
```

### `theme_blue()`

```{r}
scatter_by_species(theme_blue())
```

### `theme_red()`

```{r}
scatter_by_species(theme_red())
```

## Big Themes

### `theme_big_grid()`

```{r}
histo_by_species(theme_big_grid())
```

### `theme_big_simple()`

```{r}
histo_by_species(theme_big_simple())
```

## Palette Workflows

### Discrete palettes

```{r}
ggplot(mtcars, aes(factor(carb), fill = factor(cyl))) +
  geom_bar() +
  scale_fill_manual(values = friendly_pal("bright_seven")) +
  theme_simple()
```

You can request fewer colors than the full palette:

```{r}
friendly_pal("vibrant_seven", 3)
```

### Continuous palette interpolation

```{r}
pal <- friendly_pal("contrast_three", 50, type = "continuous")
image(volcano, col = pal)
```

## Available Palettes

Use `friendly_pals` to inspect all palette names and values:

```{r}
names(friendly_pals)
friendly_pals$ito_seven
```
